Annotation-Based Empirical Performance Tuning Using Orio

### 2009-02-12 doc/papers/ipdps09/motivation.tex
git-svn-id: https://svn.mcs.anl.gov/repos/performance/orio@428 e7ad4b5f-b827-0410-872f-f7f4bc3d1efb

The size and complexity of scientific computations are increasing at least as
fast as the improvements in processor technology.  Programming such
scientific applications is hard, and optimizing them for high performance is
even harder.  This results in a potentially large gap between the achieved
performance of applications and the peak available performance, with
many applications achieving 10\% or less of the peak (e.g.,~
%\cite{Oliker,
\cite{conf/vecpar/CarterOS06}).  
A greater concern is the inability of existing languages, compilers, and
systems to deliver the available performance for the application through
fully automated code optimizations.

>>>>

The size and complexity of scientific computations are increasing at
least as fast as the improvements in processor technology.
Programming such scientific applications is hard, and optimizing them
for high performance is even harder.  This results in a potentially
large gap between the achieved performance of applications and the
peak available performance, with many applications achieving 10\% or
less of the peak (e.g.,~\cite{Oliker,conf/vecpar/CarterOS06}).  A
greater concern is the inability of existing languages, compilers, and
systems to deliver the available performance for the application
through fully automated code optimizations.

### 2009-02-12 doc/papers/ipdps09/paper.tex
git-svn-id: https://svn.mcs.anl.gov/repos/performance/orio@428 e7ad4b5f-b827-0410-872f-f7f4bc3d1efb

\documentclass[12pt]{article}
%\usepackage{latex8}
%\usepackage[]{rotating} 
\usepackage{ifpdf}
\usepackage{url} 
\usepackage{comment} 
\usepackage{cite} 
\usepackage{graphicx} 
\usepackage{subfigure}  
\usepackage{wrapfig}
\usepackage{times}
\usepackage{amsmath,amsthm}
\usepackage[letterpaper,margin=1in]{geometry}

\ifpdf
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\else
\DeclareGraphicsExtensions{.eps,.ps}
\fi

\newenvironment{itemizer}{\begin{itemize}\setlength{\parsep}{0cm}\setlength{\itemsep}{-.3em}}{\end{itemize}}

@@

\title{\vspace{-.6in}Annotation-Based Empirical Performance Tuning\\ Using Orio}

\author{
Albert Hartono$^1$, Boyana Norris$^2$, and P. Sadayappan$^1$ \\
{\small $^1$Ohio State University, Dept. of Computer Science and Engineering, Columbus, OH 43210}\\
{\small \texttt{\{hartonoa, saday\}@cse.ohio-state.edu}}\\
{\small $^2$Argonne National Laboratory, Mathematics and Computer Science Division, Argonne, IL 60439}\\
{\small \texttt{norris@mcs.anl.gov}}
}

@@

@@

@@

\small
\bibliographystyle{abbrv} 
\bibliography{paper}

>>>>

\documentclass[conference]{IEEEtran}

%\documentclass[12pt]{article}
%\usepackage{latex8}
%\usepackage[]{rotating} 
\usepackage{ifpdf}
\usepackage{url} 
\usepackage{comment} 
\usepackage{cite} 
\usepackage{graphicx} 
\usepackage{subfigure}  
\usepackage{wrapfig}
\usepackage{times}
\usepackage{amsmath,amsthm}

%\usepackage[letterpaper,margin=1in]{geometry}

%\ifpdf
%\DeclareGraphicsExtensions{.pdf,.png,.jpg}
%\else
%\DeclareGraphicsExtensions{.eps,.ps}
%\fi

%\newenvironment{itemizer}{\begin{itemize}\setlength{\parsep}{0cm}\setlength{\itemsep}{-.3em}}{\end{itemize}}

@@

@@

\title{Annotation-Based Empirical Performance Tuning Using Orio}

\author{
\IEEEauthorblockN{Albert Hartono} 
\IEEEauthorblockA{\small Dept. of Computer Science and Engg.\\ 
Ohio State University\\ 
Columbus, Ohio 43210--1277\\ 
Email: hartonoa@cse.ohio-state.edu} 
\and 
\IEEEauthorblockN{Boyana Norris} 
\IEEEauthorblockA{\small Mathematics and Computer Science Division\\ 
Argonne National Laboratory\\ 
Argonne, Illinois 60439--4844\\
Email: norris@mcs.anl.gov} 
\and 
\IEEEauthorblockN{P. Sadayappan} 
\IEEEauthorblockA{\small Dept. of Computer Science and Engg.\\ 
Ohio State University\\ 
Columbus, Ohio 43210--1277\\ 
Email: saday@cse.ohio-state.edu}
}

@@

\IEEEpeerreviewmaketitle

@@

\section*{Acknowledgment} 
The authors would like to thank Uday Bondhugula of IBM Research for
many productive discussions and his valuable help with Pluto. This
work was supported in part by the U.S. Dept. of Energy under Contract
DE-AC02-06CH11357.

\small
\bibliographystyle{IEEEtran} 
\bibliography{IEEEabrv,paper}
